---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# ipmisc

[![packageversion](https://img.shields.io/badge/Package%20version-0.0.1-orange.svg?style=flat-square)](commits/master)
[![Travis Build Status](https://travis-ci.org/IndrajeetPatil/ipmisc.svg?branch=master)](https://travis-ci.org/IndrajeetPatil/ipmisc) 
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/IndrajeetPatil/ipmisc?branch=master&svg=true)](https://ci.appveyor.com/project/IndrajeetPatil/ipmisc) 
[![Coverage Status](https://img.shields.io/codecov/c/github/IndrajeetPatil/ipmisc/master.svg)](https://codecov.io/github/IndrajeetPatil/ipmisc?branch=master)
[![Licence](https://img.shields.io/badge/licence-GPL--3-blue.svg)](https://www.gnu.org/licenses/gpl-3.0.en.html)
[![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-', '--', Sys.Date())`-yellowgreen.svg)](/commits/master)
[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![minimal R version](https://img.shields.io/badge/R%3E%3D-3.5.0-6666ff.svg)](https://cran.r-project.org/)

## Overview

The goal of `ipmisc` is to gather miscellaneous helper functions that are
helpful for data cleaning and formatting.

It is primarily used in the following packages:

  - `ggstatsplot`: <https://indrajeetpatil.github.io/ggstatsplot/>
  - `statsExpressions`: <https://indrajeetpatil.github.io/statsExpressions/>
  - `pairwiseComparisons`:
    <https://indrajeetpatil.github.io/pairwiseComparisons/>
  - `groupedstats`: <https://indrajeetpatil.github.io/groupedstats/>

## Installation

You can install `ipmisc` from `GitHub` with:

```{r installation, eval = FALSE}
# install.packages("remotes")
remotes::install_github("IndrajeetPatil/ipmisc")
```

## Code of Conduct

Please note that the `ipmisc` project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/1/0/0/CODE_OF_CONDUCT.html). 
By contributing to this project, you agree to abide by its terms.

