---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE, warning = FALSE, messsage = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  dpi = 200,
  out.width = "100%",
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

# `ipmisc`: Miscellaneous Functions for Data Cleaning and Analysis

[![CRAN_Release_Badge](http://www.r-pkg.org/badges/version-ago/ipmisc)](https://CRAN.R-project.org/package=ipmisc)
[![Daily downloads badge](https://cranlogs.r-pkg.org/badges/last-day/ipmisc?color=blue)](https://CRAN.R-project.org/package=ipmisc)
[![Weekly downloads badge](https://cranlogs.r-pkg.org/badges/last-week/ipmisc?color=blue)](https://CRAN.R-project.org/package=ipmisc)
[![Monthly downloads badge](https://cranlogs.r-pkg.org/badges/last-month/ipmisc?color=blue)](https://CRAN.R-project.org/package=ipmisc)
[![Total downloads badge](https://cranlogs.r-pkg.org/badges/grand-total/ipmisc?color=blue)](https://CRAN.R-project.org/package=ipmisc)
[![Travis Build Status](https://travis-ci.org/IndrajeetPatil/ipmisc.svg?branch=master)](https://travis-ci.org/IndrajeetPatil/ipmisc) 
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/IndrajeetPatil/ipmisc?branch=master&svg=true)](https://ci.appveyor.com/project/IndrajeetPatil/ipmisc) 
[![Licence](https://img.shields.io/badge/licence-GPL--3-blue.svg)](https://www.gnu.org/licenses/gpl-3.0.en.html)
[![Project Status: Active - The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)
[![lifecycle](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/)
[![minimal R version](https://img.shields.io/badge/R%3E%3D-3.5.0-6666ff.svg)](https://cran.r-project.org/)
[![Coverage Status](https://img.shields.io/codecov/c/github/IndrajeetPatil/ipmisc/master.svg)](https://codecov.io/github/IndrajeetPatil/ipmisc?branch=master)
[![Coverage Status](https://coveralls.io/repos/github/IndrajeetPatil/ipmisc/badge.svg?branch=master)](https://coveralls.io/github/IndrajeetPatil/ipmisc?branch=master)
[![status](https://tinyverse.netlify.com/badge/ipmisc)](https://CRAN.R-project.org/package=ipmisc)

## Overview

The `ipmisc` provides functions for data cleaning and formatting. These
functions form data cleaning backend for the following packages:

  - `ggstatsplot`: <https://indrajeetpatil.github.io/ggstatsplot/>
  - `statsExpressions`: <https://indrajeetpatil.github.io/statsExpressions/>
  - `pairwiseComparisons`:
    <https://indrajeetpatil.github.io/pairwiseComparisons/>
  - `groupedstats`: <https://indrajeetpatil.github.io/groupedstats/>

## Installation

You can install the development version of `ipmisc` from `GitHub` with:

```{r installation, eval = FALSE}
# install.packages("remotes")
remotes::install_github("IndrajeetPatil/ipmisc")
```

## Code of Conduct

Please note that the `ipmisc` project is released with a [Contributor Code of Conduct](https://github.com/IndrajeetPatil/ipmisc/blob/master/CODE_OF_CONDUCT.md). 
By contributing to this project, you agree to abide by its terms.

