---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE, warning = FALSE, messsage = FALSE}
# show me all columns
options(tibble.width = Inf)
knitr::opts_chunk$set(
  collapse = TRUE,
  dpi = 300,
  out.width = "100%",
  comment = "#>",
  warning = FALSE,
  message = FALSE,
  fig.path = "man/figures/README-"
)
```

# `ipmisc`: Miscellaneous Functions for Data Cleaning and Analysis

[![CRAN_Release_Badge](https://www.r-pkg.org/badges/version-ago/ipmisc)](https://CRAN.R-project.org/package=ipmisc)
[![Total downloads badge](https://cranlogs.r-pkg.org/badges/grand-total/ipmisc?color=blue)](https://CRAN.R-project.org/package=ipmisc)
[![R build status](https://github.com/IndrajeetPatil/ipmisc/workflows/R-CMD-check/badge.svg)](https://github.com/IndrajeetPatil/ipmisc)
[![pkgdown](https://github.com/IndrajeetPatil/ipmisc/workflows/pkgdown/badge.svg)](https://github.com/IndrajeetPatil/ipmisc/actions)
[![Licence](https://img.shields.io/badge/licence-GPL--3-blue.svg)](https://www.gnu.org/licenses/gpl-3.0.en.html)
[![lifecycle](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://lifecycle.r-lib.org/articles/stages.html)
[![Codecov test coverage](https://codecov.io/gh/IndrajeetPatil/ipmisc/branch/master/graph/badge.svg)](https://codecov.io/gh/IndrajeetPatil/ipmisc?branch=master)


# Introduction

The `ipmisc` provides functions for data cleaning and formatting. These
functions form data cleaning backend for the following packages:

  - `ggstatsplot`: <https://indrajeetpatil.github.io/ggstatsplot/>
  - `statsExpressions`: <https://indrajeetpatil.github.io/statsExpressions/>
  - `pairwiseComparisons`: <https://indrajeetpatil.github.io/pairwiseComparisons/>
  
**Note**: The `ipmisc` functions are not expected to have much utility outside
of these packages. So, if you wish to use them, do so at your own risk. 😉

# Installation

Type | Source | Command
---|---|---
Release | CRAN | `install.packages("ipmisc")`
Development | GitHub | `remotes::install_github("IndrajeetPatil/ipmisc")`

# Functions

Function to convert a tidy data to wide data:

```{r}
library(ipmisc)

long_to_wide_converter(bugs_long, condition, desire, paired = TRUE)
```

To see all available functionality, see the documentation provided here:
<https://indrajeetpatil.github.io/ipmisc/reference/index.html>

